---
title: "Masters Homework 3"
author: "YOUR NAME HERE"
date: "7/28/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
nyc <- read.csv("https://raw.githubusercontent.com/fredlapolla/RVilcekMasters2021/main/NYC_HANES_DIAB.csv")
nyc$AGEGROUP <- factor(nyc$AGEGROUP, levels = 1:3, labels = c("Youngest", "Middle", "Aged"))
nyc$GENDER <- factor(nyc$GENDER, levels = 1:2, labels = c("male", "female"))
# Rename the HSQ_1 factor for identification
  nyc$HSQ_1 <- factor(nyc$HSQ_1, levels = 1:5, labels=c("Excellent","Very Good","Good", "Fair", "Poor"))
  # Rename the DX_DBTS as a factor
  nyc$DX_DBTS <- factor(nyc$DX_DBTS,levels = 1:3, labels=c("Diabetes with DX","Diabetes with no DX","No Diabetes"))
```


How does R treat blank values?

What command can be used to identify where NAs are located in a column?

```{r}

```


How can you use indexing to create a subset without any NAs?

```{r}

```

How could you delete a column of data, for example, the 5th 
```{r}

```


What command would let you find a set of text in the cells of a column?

```{r}

```


Rename the HSQ1 variable to Health_Status

```{r}

```

Explore the Mutate command and create a ratio of total cholesterol divided by HDL

```{r}

```



>- Why would one use a visualization for exploratory analysis?

>- What information about the nature of our data can a histogram tell us?

>- Make a histogram on your own on one column from the nyc data frame. Is it skewed? Which way? Try confirming with pastecs::stat.desc (hint set norm = TRUE as an argument).

```{r}

```

>- Try making a QQPlot to assess the normality of one variable of your choosing. Is the distribution normal? How can you tell?

```{r}

```

>- Make a boxplot glucose levels by diabetes diagnosis:

```{r}


```

